Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-11-23 Ch1_movement_rates/Ch1_Figures.Rmd
Updates on Figures

disp2_plot
ggsave2(filename = "Ch1_movement_rates/Figures/Figure4.png")

@@

Figure 5 - Dispersal for each seed and dispersal kernels

```{r fig.width=9, fig.height=3.5}

points_plot <- function(seed.data, summ.data, s.size = 50000, xylims=1250, lalpha = 0.5, scenario = NULL, twoplots = FALSE){

  # seed.data %>% 
  #   drop_na(s.id) %>% 
  #   mutate(dispcat = ifelse(disp <150, "non", 
  #                           ifelse(disp <500, "med", "ldd"))) %>% 
  #   #slice_head(., n = s.size) %>% 
  #   sample_n(s.size) %>% 
  #     ggplot(., aes(x = xloc, y = yloc, color = dispcat)) +
  #     geom_point(alpha = lalpha) +
  #     scale_color_manual(values = c(my.cols1[6], my.cols1[7], "black")) +
  #     geom_text(label = scenario, x = -1100, y = -1100, color = "black") +
  #     coord_equal(xlim = c(-xylims, xylims), ylim = c(-xylims, xylims)) +
  #     theme_bw() +
  #     theme(legend.position = "none",
  #           axis.title = element_blank()) +
  #      NULL -> seedlocplot

  seed.data %>% 
    drop_na(s.id) %>% 
    mutate(LDD = ifelse(disp <500, NA, "Over 500")) %>% 
    sample_n(s.size) %>% 
      ggplot(., aes(x = xloc, 
                    y = yloc
                    , color = LDD
                    )) +
      geom_hex()+
      scale_fill_gradient(low = "grey", high = "black") +
      #geom_point(alpha = lalpha) +
      scale_color_manual(values = c(my.cols1[6], my.cols1[7])) +
      geom_text(label = scenario, x = -1100, y = -1100, color = "black") +
      coord_equal(xlim = c(-xylims, xylims), ylim = c(-xylims, xylims)) +
      theme_bw() +
      theme(legend.position = "none",
            axis.title = element_blank()) +
       NULL -> seedlocplot

    if(twoplots == TRUE){

          summ.data %>% 
    #drop_na(s.id) %>% 
    mutate(dispcat = ifelse(av.disp <500, "non", "Over 500")) %>% 
    #slice_head(., n = s.size) %>% 
    sample_n(s.size*5) %>% 
      ggplot(., aes(x = x, y = y, color = dispcat)) +
      geom_point(alpha = lalpha) +
      labs(subtitle = scenario) +
      scale_color_manual(values = c(my.cols1[6], my.cols1[7])) +
      coord_equal(xlim = c(-xylims, xylims), ylim = c(-xylims, xylims)) +
      theme_bw() +
      theme(legend.position = "none",
            axis.title = element_blank()) +
       NULL -> summaryplot

      plot_grid(seedlocplot, summaryplot, ncol = 2)
    }

  else{seedlocplot}
}

# A <- points_plot(seed.data = cp.df, summ.data = cp.summ.df, scenario = "CP", twoplots = TRUE)
# A

A <- points_plot(seed.data = cp.df, summ.data = cp.summ.df, scenario = "CP")
B <- points_plot(seed.data = pp.df, summ.data = pp.summ.df, scenario = "PP")
C <- points_plot(seed.data = np.df, summ.data = np.summ.df, scenario = "NP")

@@

legend <- get_legend(C + scale_fill_gradient(low = "grey", high = "black",
                                             name = "Count",
                          guide = guide_colorbar(barwidth = 15, 
                                                barheight = 0.5,
                                                title.position = "left",
                                                title.vjust = 1.1,
                                                 #label.position = "left",
                                                 nbin = 100)) +
  scale_color_manual(values = c(LDD = my.cols1[6]), name = "")+
    guides(color = guide_legend(override.aes = list(fill = my.cols1[6]))) +
    theme(legend.position = "bottom"))

seedplots2d <- plot_grid(prow, legend, rel_heights = c(1,0.1), ncol = 1)
#seedplots2d

```{r fig.height=7.5, fig.width=9, eval = FALSE}
plot_grid(seedplots2d, NULL, disp2_plot, nrow = 3, rel_heights = c(1,0.2,1))

@@

```{r results='hide'}

>>>>

# disp2_plot
# ggsave2(filename = "Ch1_movement_rates/Figures/Figure4.png")

@@

```{r}
points_plot <- function(seed.data, s.size = 50000, xylims=1250, scenario = NULL, lalpha = 0.5){

  seed.data %>% 
    drop_na(s.id) %>% 
    mutate(LDD = ifelse(disp <500, NA, "Over 500m")) %>% 
    sample_n(s.size) %>% 
      ggplot(., aes(x = xloc, 
                    y = yloc
                    , color = LDD
                    )) +
      geom_hex()+
      scale_fill_gradient(low = "grey", high = "black") +
      #geom_point(alpha = lalpha) +
      scale_color_manual(values = my.cols1[6], na.translate = F) +
      geom_text(label = scenario, x = -1100, y = -1100, color = "black") +
      coord_equal(xlim = c(-xylims, xylims), ylim = c(-xylims, xylims)) +
      theme_bw() +
      theme(legend.position = "none",
            axis.title = element_blank()) +
       NULL
}
```

```{r fig.width=9, fig.height=3.5}
A <- points_plot(seed.data = cp.summ.df %>% 
              mutate(disp = av.disp,
                     s.id = run,
                     xloc = x,
                     yloc = y), scenario = "CP")
B <- points_plot(seed.data = pp.summ.df %>% 
              mutate(disp = av.disp,
                     s.id = id,
                     xloc = x,
                     yloc = y), scenario = "PP")
C <- points_plot(seed.data = np.summ.df %>% 
              mutate(disp = av.disp,
                     s.id = id,
                     xloc = x,
                     yloc = y), scenario = "NP")
prowB <- plot_grid(A, B, C, ncol = 3)
legend <- get_legend(C + theme(legend.position = "bottom") +
  scale_fill_gradient(low = "lightgray", high = "black",
                                             name = "Count",
                          guide = guide_colorbar(barwidth = 15, 
                                                barheight = 0.5,
                                                title.position = "left",
                                                title.vjust = 1.1,
                                                 #label.position = "left",
                                                 nbin = 100)) +
    guides(color = guide_legend(title = element_blank(),override.aes = list(fill = "lightgray",
                                                                            size = 5), direction = "horizontal")))
hexplot <- plot_grid(prowB, legend, rel_heights = c(1,0.1), ncol = 1, labels = c("C)"), hjust = 0, vjust = 1, label_size = 10)

```{r fig.height=7.5, fig.width=9}
plot_grid(disp2_plot, NULL, hexplot, nrow = 3, rel_heights = c(1,0.05,1))

Figure 5 - Dispersal kernels

```{r fig.width=9, fig.height=3.5, eval = FALSE}

A <- points_plot(seed.data = cp.df, scenario = "CP")
B <- points_plot(seed.data = pp.df, scenario = "PP")
C <- points_plot(seed.data = np.df, scenario = "NP")

@@

legend <- get_legend(C + theme(legend.position = "bottom") +
  scale_fill_gradient(low = "lightgray", high = "black",
                                             name = "Count",
                          guide = guide_colorbar(barwidth = 15, 
                                                barheight = 0.5,
                                                title.position = "left",
                                                title.vjust = 1.1,
                                                 #label.position = "left",
                                                 nbin = 100)) +
    guides(color = guide_legend(title = element_blank(),override.aes = list(fill = "lightgray",
                                                                            size = 5), direction = "horizontal")))

seedplots2d <- plot_grid(prow, legend, rel_heights = c(1,0.1), ncol = 1)
seedplots2d

@@

```{r include = FALSE}
